Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-06-18 Manuscript/manuscriptPSsuppl.tex
Update pdfs and update Fig. 4 caption based on the question by Tiago Ferreira in pull request https://github.com/NMRLipids/NMRlipidsIVotherHGs/pull/97
Author contribution MSM.

\section{Author contributions}
\noindent
{\it Hanne Antila}
Contiributed to the development analysis tools used for evaluating the force fields,  provided critical discussion on the manuscript content and edited it for clarity.

\noindent
{\it Pavel Buslaev}
Analyzed the dihedral angle distributions in the head group and glycerol backbone regions.

\noindent
{\it Fernando Favela-Rosales}
Setup and performed one of the DOPS simulations with Slipids.

\noindent
{\it Tiago M. Ferreira}

\noindent
{\it Ivan Gushchin}
Supervised the work of P.B.

\noindent
{\it Matti Javanainen}
Performed most of the MacRog simulations and provided comments on the manuscript.

\noindent
{\it Batuhan Kav}
Set up, performed, and analyzed Amber Lipid14/17 simulations with the Amber MD. 
\noindent
{\it Jesper J. Madsen}
Set up, performed and analyzed several of the CHARMM36 simulations. Provided comments on the manuscript.

\noindent
{\it Josef Melcr}
consulted the project, 
prepared tools for calculating order parameters
and performed several simulations.

\noindent
{\it Markus Miettinen}

\noindent
{\it Ricky Nencini}

\noindent
{\it O. H. Samuli Ollila}
Designed the project and managed the work.
Ran and analysed several simulations. Wrote the manuscript.

\noindent
{\it Thomas Piggot}
Setup, performed and analysed many of the simulations. Contributed to parts of the manuscript.

>>>>

\section{Author contributions}
\noindent
{\it Hanne Antila}
contributed to the development of analysis tools used for evaluating the force fields,  provided critical discussion on the manuscript content, and edited it for clarity.

\noindent
{\it Pavel Buslaev}
analysed the dihedral angle distributions in the head group and glycerol backbone regions.

\noindent
{\it Fernando Favela-Rosales}
set up and performed one of the DOPS simulations with Slipids.

\noindent
{\it Tiago M. Ferreira}
performed the NMR experiments and NMR simulations, processed and analysed the experimental data, prepared the corresponding figures, wrote parts of the manuscript (NMR methods and interpretation of the SDROSS results), and took part in the final revision.

\noindent
{\it Ivan Gushchin}
supervised the work of P.B.

\noindent
{\it Matti Javanainen}
performed most of the MacRog simulations, and provided comments on the manuscript.

\noindent
{\it Batuhan Kav}
set up, performed, and analysed Amber Lipid14/17 simulations with the Amber MD.

\noindent
{\it Jesper J. Madsen}
set up, performed, and analysed several of the CHARMM36 simulations. Provided comments on the manuscript.

\noindent
{\it Josef Melcr}
consulted the project, 
prepared tools for calculating order parameters,
and performed several simulations.

\noindent
{\it Markus S. Miettinen}
worked with
H. A. on the analysis tools, and with
B. K. on the Amber MD simulations.
Made the subjective force field ranking.
Edited the manuscript.

\noindent
{\it Ricky Nencini}
ran the simulations of POPC systems using CHARMM36 with and without NB-Fix, and contributed to the discussion on system/bulk concentration.

\noindent
{\it O. H. Samuli Ollila}
designed the project and managed the work.
Ran and analysed several simulations. Wrote the manuscript.

\noindent
{\it Thomas J. Piggot}
set up, performed, and analysed many of the simulations. Contributed to parts of the manuscript.
